### 2020-02-13 README.Rmd
bugfix

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# hashuri

@@

`hashuri` seeks to make it easy to adopt data workflows that are based around the [hash-uri specification](https://github.com/hash-uri/hash-uri) for content-addressable storage. This very simple idea can be used to address several challenging problems in data management.

```{r eval=FALSE}
remotes::install_github("cboettig/hashuri")
```

@@

```{r}
vostok_co2 <- system.file("extdata", "vostok.icecore.co2", package = "hashuri")
readLines(vostok_co2, n = 25)
```

@@

Frequently we access data resources from the internet instead.  For instance, the file in question was downloaded from <http://cdiac.ornl.gov/ftp/trends/co2/vostok.icecore.co2>.  We can download this file locally and confirm it creates the same identifier (equivalent to comparing the file checksum, but using the checksum as the identifier makes it harder to overlook this step!).  `hashuri` can also let us register the URL at which we found the data in a hash archive, <https://hash-archive.org>.

```{r}
co2_url <- "http://cdiac.ornl.gov/ftp/trends/co2/vostok.icecore.co2"
remote_register(co2_url)
```

@@

```{r}
remote_lookup("hash://sha256/9412325831dab22aeebdd674b6eb53ba6b7bdd04bb99a4dbb21ddff646287e37")
```

@@

One application of `hashuri` is to support robust access of data files in R packages.  One of the most common approaches remains the distribution of data directly inside an R package, as in our example above.  This is not ideal for many reasons.  However, packages that rely on remote access of data risk link rot of those download URLs (e.g. there is not a simple and universal mechanism for resolving download URLs from DOIs, and many sources lack DOIs anyway).  Such R packages could instead register the current links in a hash archive, allowing package or analysis code to refer directly to the hash uri rather than a link that might rot.  (Clearly this resolving step still depends on the existence of some robust hash archive, a role scientific repositories could easily fill. Note the hash archive is merely a look-up table, it does not need to store any actual content).

@@

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
Sys.setenv("CONTENTURI_HOME"= tempdir())
```

# contenturi

@@

`contenturi` seeks to make it easy to adopt data workflows that are based around the [hash-uri specification](https://github.com/hash-uri/hash-uri) for content-addressable storage. This very simple idea can be used to address several challenging problems in data management.

```{r eval=FALSE}
remotes::install_github("cboettig/contenturi")
```

@@

```{r}
vostok_co2 <- system.file("extdata", "vostok.icecore.co2", package = "contenturi")
readLines(vostok_co2, n = 25)
```

@@

Frequently we access data resources from the internet instead.  For instance, the file in question was downloaded from <http://cdiac.ornl.gov/ftp/trends/co2/vostok.icecore.co2>.  We can download this file locally and confirm it creates the same identifier (equivalent to comparing the file checksum, but using the checksum as the identifier makes it harder to overlook this step!).  `contenturi` can also let us register the URL at which we found the data in a hash archive, <https://hash-archive.org>.

```{r}
co2_url <- "http://cdiac.ornl.gov/ftp/trends/co2/vostok.icecore.co2"
register(co2_url)
```

@@

```{r}
lookup("hash://sha256/9412325831dab22aeebdd674b6eb53ba6b7bdd04bb99a4dbb21ddff646287e37")
```

@@

One application of `contenturi` is to support robust access of data files in R packages.  One of the most common approaches remains the distribution of data directly inside an R package, as in our example above.  This is not ideal for many reasons.  However, packages that rely on remote access of data risk link rot of those download URLs (e.g. there is not a simple and universal mechanism for resolving download URLs from DOIs, and many sources lack DOIs anyway).  Such R packages could instead register the current links in a hash archive, allowing package or analysis code to refer directly to the hash uri rather than a link that might rot.  (Clearly this resolving step still depends on the existence of some robust hash archive, a role scientific repositories could easily fill. Note the hash archive is merely a look-up table, it does not need to store any actual content).

@@

```{r include = FALSE}
Sys.unsetenv("CONTENTURI_HOME")

```
